---
title: "IHC Norway Survey"
author: "Chris Rose, Folkehelseinstituttet (`r Sys.Date()`)"
output: 
  rmarkdown::word_document:
    fig_width: 7
    fig_height: 5.6
    reference_docx: template.docx
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dpi=600
)

library(fhi.ihc.norway.2019)
library(knitr)
import::from(magrittr, "%>%")

set.seed(1234)

# Get the vignette directory for saving figures.
vignette_dir <- rprojroot::find_root_file("vignettes",
                                          criterion = rprojroot::has_file("DESCRIPTION"))
```

This report was generated on `r date()` using revision
`r system("git rev-parse --short HEAD", intern = TRUE)`.

## Overview

This document describes the methods and results of the survey of Norwegians' understanding
of key concepts for Informed Health Choices.

## Methods


### Norwegians' understanding of the key concepts, attitudes, and intended behaviors

We developed four different questionnaires to cover 31 of the key concepts. Questions on
four concepts of particular interest ("Old is better!", "Associated with!", "A study
shows!", and "Dissimilar comparison groups") were included in all questionnaires. The
first questionnaire included translations into Norwegian Bokmål of the same questions used
in our previous randomized controlled trials in Uganda, facilitating comparison of
Norwegians and Ugandans (see below). We used survey responses to estimate the percentage
of the adult Norwegian population that understands each concept, and that agrees with each
of seven statements about attitudes and intended behaviors. We classified a participant as
understanding a concept if they correctly answered all questions on the concept.

To address the likely problem of non-random non-response, we used iterative
post-stratification to match marginal distributions of sex, educational attainment level,
and statistical region of residence of the sample to the Norwegian population, as
described below. We did not collect data on participant age and could not use it for
post-stratification as planned.

We obtained Eurostat data on the marginal distributions of sex and statistical region of
residence for all Norwegians, and educational attainment level for Norwegians aged 15 to
64 years (data sets `TPS00002`, `TGS00096`, and `edat_lfse_03`). Participants reported
their "fylke" (county) of residence. We mapped these to the corresponding Nomenclature of
Territorial Units for Statistics (NUTS 2) regions of Norway reported by Eurostat.
Participants reported the highest level of education they attained using Norwegian
terminology (e.g., "Grunnskolen", "Videregående"). We mapped these to the corresponding
International Standard Classification of Education 2011 categories reported by Eurostat
(levels 0–2, 3–4, and 5–8). We then used multiple imputation using chained equations to
account for missing values of the post-stratification variables. We performed
imputation using: the post-stratification variables (sex, region of residence,
and educational attainment); demographic variables that code for whether participants
had training in research or medicine, or if they had been a research participant;
and the dependent variable (whether they understood a particular concept). We iteratively
post-stratified each imputed data set and estimated the percentage of the Norwegian
population that understands each key concept, and that agrees with each of statements
about attitudes and intended behaviors. We used the R packages `mice`, `mitools`,
`survey`, and `tidyverse`.

We present summaries of the sample (numbers, sample sizes, and percentages) and
post-stratified population estimates for the 31 key concepts, and seven attitudes and
intended behaviors. We quantified uncertainty on our estimates using 95% confidence
intervals, and protected the family-wise coverage probability of the confidence intervals
for the four key concepts included in all questionnaires via Bonferroni-correction.


### Comparisons to Ugandans

We used data from the first questionnaire and our previous randomized controlled
trials in Uganda to compare mean test scores, and probabilities of achieving
passing and mastery scores, between Norwegian adults and Ugandan parents
(controls who did not listen to a podcast intervention, and took the test at the
time of the original trial), teachers (controls who took the test one year after
the original trial), and children (assigned either to a podcast intervention or
a control group, and who took the test one year after the original trial). We
defined passing as answering at least 13 of 24 questions correctly (at least 11
of 18 for Ugandan parents), and mastery as answering at least 20 of 24 questions
correctly (at least 15 of 18 for Ugandan parents), as in the original trials.

We estimated mean scores and odds ratios using generalized linear mixed-effects
models (GLMMs; normal errors and identity link for mean scores, binomial errors
and logit link for passing and mastery) using the `lme4` R package. In the
trials, school was the randomized unit for children and teachers, while parents
were individually randomized. We modelled this clustering structure using random
effects (a random intercept for each randomized unit). We did not adjust for
other covariates. No data were missing and we did not apply post-stratification
weights for Norwegians.

For mean scores, we present a table of estimates of population means and
differences in means relative to the Ugandan children, and a forest plot of the
mean scores. For passing and mastery, we present tables of estimates of odds
ratios comparing each group to Ugandan children, probabilities ("risks",
calculated from the estimated coefficients of the GLMMs), and differences in
probabilities ("risk differences") relative to the Ugandan children. Odds ratios
less than unity and differences less than zero favor the children. We quantify
uncertainty on estimates using 95% confidence intervals and *P* values.

### Exploratory analyses

#### Key concepts

We performed exploratory analyses to investigate how Norwegians' understanding
of each key concept is associated with the demographic covariates sex, research
training, research participation, education, and medical education. We used
generalized linear models (quasibinomial errors, logit link) to model
understanding of each concept in terms of the covariates, which were modelled as
categorical variables. Multiple imputation and post-stratification were used as
in the main analysis.

#### Attitudes and intended behaviors

We also performed exploratory analyses to investigate how Norwegians' attitudes
and intended behaviors are associated with the demographic covariates sex,
research training, research participation, education, and medical education.
Analyses were performed in the same way as for the exploratory analyses for the
key concepts.

#### Mean score, passing, and mastery

We used data from the first questionnaire to perform exploratory analyses to
investigate how Norwegians' mean scores and achievement of passing and mastery
scores are associated with the demographic covariates sex, research training,
research participation, education, and medical education. We used generalized
linear models (normal errors and identity link for mean score; quasibinomial
errors and logit link for passing and mastery) to model the outcomes in terms of
the covariates, which were modelled as categorical variables. Multiple
imputation and post-stratification were used as in the main analysis. We
performed imputation using: the post-stratification variables (sex, region of
residence, and educational attainment); demographic variables that code for
whether participants had training in research or medicine, and if they had
been a research participant; and mean score (which is directly related to the
outcomes passing and mastery).


## Results

### Participant characteristics

The following table shows participant characteristics across the four
questionnaires. For each level of each stratification variable, Fisher's exact
test is used to assess the strength evidence against the null hypothesis of
equal proportions across the four questionnaires (**NOTE:** this column is for
information only and may be dropped from the final table). Of the 771
respondents, 21 (2.7%) did not provide data on at least of one the covariates
sex, research training, research participation, education, medical education,
and county of residence.

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
table_participants() %>% kable()
```


### Norwegians' understanding of the key concepts, attitudes, and intended behaviors

#### Key concepts

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
# Calculate the proportions for each concept.
understand_concepts_result <- proportion_understand_all_concepts()

# Calculate the mean, minimum and maximum half-widths of the CIs for
# concepts that are and are not Bonferroni-corrected, and the number of
# CIs that were too wide.
common_ind <- stringr::str_ends(understand_concepts_result$concept, "\U2021")
other_ind <- !common_ind

mean_common <- mean(understand_concepts_result$half_width[common_ind]) %>% scales::percent()
min_common <- min(understand_concepts_result$half_width[common_ind]) %>% scales::percent()
max_common <- max(understand_concepts_result$half_width[common_ind]) %>% scales::percent()

mean_other <- mean(understand_concepts_result$half_width[other_ind]) %>% scales::percent()
min_other <- min(understand_concepts_result$half_width[other_ind]) %>% scales::percent()
max_other <- max(understand_concepts_result$half_width[other_ind]) %>% scales::percent()

num_ci_too_wide <- sum(understand_concepts_result$half_width > 0.08)

# Stop if the powering was not successful on average overall.
stopifnot(mean(understand_concepts_result$half_width) < 0.08)
```

We designed the survey to provide estimates of Norwegians' understanding of the key
concepts with confidence intervals no wider than ±5% (for the four concepts common to all
questionnaires) and ±8% (for the other concepts, and the attitudes and intended
behaviors). This was achieved on average, but not for every concept. The mean width of the
confidence intervals for the four concepts common to all questionnaires was
±`r mean_common` (range ±`r min_common` to ±`r max_common`). The mean width of the other
confidence intervals was ±`r mean_other` (range ±`r min_other` to ±`r max_other`;
`r num_ci_too_wide` of the `r length(understand_concepts_result$half_width)` concepts had
confidence intervals wider than ±8%).

The following table shows estimates of the percentage of the Norwergian population that
understands each of the key concepts.

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
understand_concepts_result %>% summary() %>% kable()
```
‡ Confidence intervals have been Bonferroni-corrected.

The above results are presented graphically in the figure below:

```{r echo=FALSE, message=FALSE, fig.width = 9, fig.height = 10}
understand_concepts_result %>% plot()
ggplot2::ggsave(file.path(vignette_dir, "understand-concepts.png"), width = 9, height = 10, dpi = 600)
```

#### Attitudes and intended behaviors

The following table shows estimates for attitudes and intended behaviors.

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
attitudes_result <- proportion_understand_all_concepts(attitudes_intentions = TRUE)
attitudes_result %>% summary() %>% kable()
```

The above results are presented graphically in the figure below.

```{r echo=FALSE, message=FALSE, fig.width = 9, fig.height = 3}
attitudes_result %>% plot()
ggplot2::ggsave(file.path(vignette_dir, "attitudes.png"), width = 9, height = 3, dpi = 600)
```


### Comparisons to Ugandans

#### Mean score

The following table compares mean test scores of Norwegians and Ugandans parents.

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
mean_score_result <- num_correct_glmm_analysis(formula = proportion_correct ~ group + (1|school),
                                               family = stats::gaussian(link = "identity"))
mean_score_result %>% summary() %>% kable()
```

The above results are presented graphically in the figure below.

```{r echo=FALSE, message=FALSE, fig.width = 10, fig.height = 2}
mean_score_result %>% plot()
ggplot2::ggsave(file.path(vignette_dir, "mean-score.pdf"))
```

#### Passing

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
passing_result <- num_correct_glmm_analysis(formula = passing ~ group + (1|school),
                                            family = stats::binomial(link = "logit"))
passing_result %>% summary() %>% kable()
```

The above results are presented graphically in the figure below.

```{r echo=FALSE, message=FALSE, fig.width = 11, fig.height = 2}
passing_result %>% plot()
ggplot2::ggsave(file.path(vignette_dir, "passing.pdf"))
```

#### Mastery

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
mastery_result <- num_correct_glmm_analysis(formula = mastery ~ group + (1|school),
                                            family = stats::binomial(link = "logit"))
mastery_result %>% summary() %>% kable()
```

The above results are presented graphically in the figure below.

```{r echo=FALSE, message=FALSE, fig.width = 11, fig.height = 2}
mastery_result %>% plot()
ggplot2::ggsave(file.path(vignette_dir, "mastery.pdf"))
```

### Exploratory analyses

#### Key concepts

The following table presents the results of the analysis performed to explore
associations between demographic covariates and Norwegians' understanding of the key
concepts. Results are presented as odds ratios. Odds ratios greater than unity
indicate that a covariate is associated with better understanding.

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
logistic_regression_result <- regression_all_concepts()
```

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
example_estimate <- logistic_regression_result %>% 
  summary() %>% 
  {.[.$` ` == concepts$subgroups_misleading, "Intercept"]} %>%
  as.character()
```

Note that some odds ratios are clearly misestimated for some concepts. For
example, the intercept term for the concept 
"`r concepts$subgroups_misleading`" (i.e., a "reference" individual's odds for
understanding the concept) is estimated to be `r example_estimate`.
Formal testing for collinearity, singularity, outliers, and goodness of fit
failed to identify these specific problems, however visual inspection of the data
suggests that the problem may be explained by collinearity between the dependent
variable (understanding the concept) and education (ISCED level).

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
logistic_regression_result %>% summary() %>% kable()
```

The results in the table above are presented graphically below. Note that
confidence intervals extending outside axis ranges are clipped.

```{r echo=FALSE, , fig.width = 12.5, fig.height = 7.5, message=FALSE, warning=FALSE}
logistic_regression_result %>% plot()
ggplot2::ggsave(file.path(vignette_dir, "exploratory-concepts.pdf"))
```

#### Attitudes and intended behaviors

The following table presents the results of analyses performed to explore the
associations between demographic covariates and Norwegians' attitudes and intended
behaviors. Results are presented as odds ratios. Odds ratios greater than unity
indicate that a covariate is associated with having a particular attitude or
intending to engage in a particular behavior.

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
attitudes_logistic_regression_result <- regression_all_concepts(attitudes_intentions = TRUE)
```

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
example_estimate <- attitudes_logistic_regression_result %>% 
  summary() %>% 
  {.[.$` ` == attitudes$att_se_15_1, "ISCED Levels 3-4"]} %>%
  as.character()
```

As before, some odds ratios are clearly misestimated. For example, the odds
ratio for ISCED Levels 3-4 for the attitude 
"`r attitudes$att_se_15_1`" is estimated to be `r example_estimate`.
As before, this problem may be explained by collinearity between the dependent
variable (understanding the concept) and education (ISCED level).

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
attitudes_logistic_regression_result %>% summary() %>% kable()
```

The results in the table above are presented graphically below. Note that
confidence intervals extending outside axis ranges are clipped.

```{r echo=FALSE, fig.height=2, fig.width=11, message=FALSE, warning=FALSE}
attitudes_logistic_regression_result %>% plot()
ggplot2::ggsave(file.path(vignette_dir, "exploratory-attitudes.pdf"))
```

#### Mean score, passing, and mastery

The following table presents the results of analyses performed to explore the
associations between demographic covariates and Norwegians' mean scores and
achievement of passing and mastery scores. Results for mean score are presented as
percentages. Results for passing and mastery are presented as odds ratios. Odds
ratios greater than unity indicate that a covariate is associated with achieving
passing or mastery scores.

Note that the result for passing is unreliable because all but one of the
Norwegian respondents achieved a passing score. The one Norwegian who did not
achieve a passing score was not educated past primary school level (ISCED levels
0-2), did not have education in research or medicine, and had been a research
participant.

```{r echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
exploratory_mean_score <- exploratory_regression_norwegians(
                            outcome = "num_correct / num_total",
                            outcome_name = "Mean score",
                            family = stats::gaussian())
exploratory_passing     <- exploratory_regression_norwegians(
                            outcome = "passing",
                            outcome_name = "Passing",
                            family = stats::quasibinomial(link = "logit"))
exploratory_mastery     <- exploratory_regression_norwegians(
                            outcome = "mastery",
                            outcome_name = "Mastery",
                            family = stats::quasibinomial(link = "logit"))
rbind(
  exploratory_mean_score  %>% summary(),
  exploratory_passing     %>% summary(),
  exploratory_mastery     %>% summary()
) %>% kable()
```
